### 2016-11-17 paper/evaluation.tex
fixed piecharts and updated plots

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.4\textwidth]{results/rq1/plots/piechart.pdf}
    \caption{\label{fig:piechart-time} Subjects grouped by elapsed
    time on test execution ($t$): short execution ($t < 1m$), medium 
    execution ($1m \leq t < 5m$), and long execution ($5m \leq t$).
    \Fix{On the left side, results from sequential execution; on the
    right side, results from default execution.}}
\end{figure}

Considering the groups \emph{medium} and \emph{long} (\Fix{X}
subjects), we investigated the relationship between the number of
tests cases and the time cost from subjects.  Figure~\ref{fig:scatter}
shows two scatter plots with We created a scatter plot for each group
and computed the correlation of time cost and number of tests.
\Fix{elaborate: As expected, Figure~\ref{fig:scatters} reveals that
the number of tests cases are not related to the elapsed time.
\Fix{explain briefly what dominates a test execution/types of tests}.
We ignored outliers for better visualization.} Results indicate that
\Fix{...conclusion...}.

\begin{figure}[h!]%
    \centering
    \begin{minipage}{0.5\textwidth}
        \subfigure[\Fix{medium}]{
            \includegraphics[width=\textwidth]{results/rq1/plots/scatterplot-med.pdf}
        }\\
        \subfigure[\Fix{long}]{
            \includegraphics[width=\textwidth]{results/rq1/plots/scatterplot-long.pdf}
        }%
    \end{minipage}%
    \caption{\Fix{...use minutes instead of secs...}}%
    \label{fig:scatters}%
\end{figure}

@@

\begin{itemize}
    \item \RQB
\end{itemize}

@@

\begin{figure}[h!]
   \centering
   \includegraphics[width=0.4\textwidth]{results/plots/parallelism-settings.pdf}
   \caption{\Fix{...}}
\end{figure}

>>>>

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.48\textwidth]{results/plots/piechart-timecost.pdf}
    \caption{\label{fig:piechart-time} Subjects grouped by elapsed time on test
    execution ($t$): short execution ($t < 1m$), medium execution ($1m \leq t <
    5m$), and long execution ($5m \leq t$).  On the left side, results from
    sequential execution; on the right side, results from default execution.}
\end{figure}

Considering the groups \emph{medium} and \emph{long} (\Fix{X}
subjects), we investigated the relationship between the number of
tests cases and the time cost from subjects.  Figure~\ref{fig:scatters}
shows two scatter plots with We created a scatter plot for each group
and computed the correlation of time cost and number of tests.
\Fix{elaborate: As expected, Figure~\ref{fig:scatters} reveals that
the number of tests cases are not related to the elapsed time.
\Fix{explain briefly what dominates a test execution/types of tests}.
We ignored outliers for better visualization.} Results indicate that
\Fix{...conclusion...}.

\begin{figure}[h!]%
    \centering
    \Fix{scatter top, scatter bottom, legend r-value regression}
    \caption{\Fix{...use minutes instead of secs...}}%
    \label{fig:scatters}%
\end{figure}

@@

\begin{itemize}
    \item \emph{\RQB}
\end{itemize}

@@

\begin{figure}[h!]
   \centering
   \caption{\Fix{...}}
\end{figure}
